---
title: "Chapter 12 Maps"
author: Robert Dinterman
date: "`r format(Sys.Date(), '%Y-%B-%d')`"
output:
  md_document:
    variant: markdown_github
---

```{r start, include = FALSE}
#devtools::install_github("rdinter/albersusa")
library("albersusa")
library("gganimate")
library("knitr")
library("lubridate")
library("maptools")
library("scales")
library("sp")
library("spdplyr")
library("tidyverse")

local_dir   <- "../2-eda"
figures     <- paste0(local_dir, "/figures")
if (!file.exists(local_dir)) dir.create(local_dir)
if (!file.exists(figures)) dir.create(figures)

qtrly_data <- read_rds("../0-data/uscourts/f2_three/f2_three.rds") %>% 
  mutate(quarter = quarter(DATE))
farms <- read_csv("../0-data/nass/operations_state.csv")
farms_county <- read_csv("../0-data/nass/operations_county.csv",
                         col_types = cols(.default = "d"))

banks <- farms %>% 
  select(farms_state = FARMS, YEAR, STATE) %>% 
  bind_rows(data.frame(farms_state = 100,
                       YEAR = as.numeric(unique(farms$YEAR)),
                       STATE = "DISTRICT OF COLUMBIA")) %>% 
  right_join(qtrly_data)

dist_hacks <- data.frame(FIPS = c(2010, 46102),
                         COUNTY = c("", "OGLALA LAKOTA"),
                         STATE = c("ALASKA", "SOUTH DAKOTA"),
                         DISTRICT = c("ALASKA", "SOUTH DAKOTA"),
                         CIRCUIT = c("NINTH CIRCUIT", "EIGHTH CIRCUIT"))
dists <- read_csv("../0-data/uscourts/district_counties.csv") %>% 
  mutate(FIPS = as.numeric(FIPS),
         fips = as.numeric(FIPS)) %>% 
  bind_rows(dist_hacks)

dist_map <- dists %>%
  group_by(STATE) %>% 
  summarise(STATE_DISTS = n_distinct(DISTRICT)) %>% 
  right_join(dists)

# Merge in with county level data, then aggregate to district level
j5 <- farms_county %>% 
  left_join(dist_map) %>% 
  group_by(YEAR, DISTRICT, STATE_DISTS, STATE, CIRCUIT) %>% 
  summarise(FARMS = sum(FARMS, na.rm = T)) %>% 
  # Need to add in a row for DC:
  bind_rows(data.frame(YEAR = unique(farms_county$YEAR),
                       DISTRICT = "DISTRICT OF COLUMBIA",
                       STATE = "DISTRICT OF COLUMBIA",
                       CIRCUIT = "DC CIRCUIT", FARMS = 100,
                       STATE_DISTS = 1)) %>% 
  ungroup()

hi <- j5 %>%
  group_by(STATE, YEAR) %>%
  summarise(state_farms = sum(FARMS, na.rm = T)) %>% 
  right_join(j5) %>% 
  mutate(ratio = FARMS / state_farms) %>% select(-state_farms)

j6 <- hi %>% 
  select(YEAR, DISTRICT, STATE, STATE_DISTS, CIRCUIT, ratio) %>% 
  right_join(banks) %>% 
  mutate(farms_impute = round(ratio*farms_state)) %>% 
  fill(farms_impute, farms_state) %>% 
  fill(farms_impute, farms_state, .direction = "up")

### Map Data
first <- counties_composite("aeqd")

first <- merge(first, dists)

gg_base <- fortify(first, region = "DISTRICT") %>%
  rename(DISTRICT = id)


# Add in aggregated data ...
gg_first_bapcpa <- j6 %>% 
  filter(YEAR > 2005) %>% 
  group_by(DISTRICT) %>% 
  summarise(b_rate = 4*(10000)*sum(impute, na.rm = T) /
              sum(farms_impute, na.rm = T),
            CHAP_12 = sum(impute, na.rm = T),
            farms  = mean(farms_impute, na.rm = T)) %>%
  right_join(gg_base)


states  <- usa_composite("aeqd")
states <- data.frame(toupper(states$name), coordinates(states),
                     stringsAsFactors = F)
names(states) <- c("id", "x", "y")
states_bapcpa <- j6 %>% 
  filter(YEAR > 2005) %>% 
  rename(id = STATE) %>% 
  group_by(id) %>% 
  summarise(b_rate = 4*(10000)*sum(impute, na.rm = T) /
              sum(farms_impute, na.rm = T),
            CHAP_12 = sum(impute, na.rm = T)) %>%
  right_join(states)
gg_state_bapcpa <- first %>% 
  fortify(region = "STATE") %>% 
  left_join(states_bapcpa)

# Remove the new england states
new_england <- c("CONNECTICUT", "RHODE ISLAND", "VERMONT",
                 "DISTRICT OF COLUMBIA", "DELAWARE")

bank_theme <-   theme(panel.background = element_rect(fill = "transparent"),
                      panel.grid = element_blank(),
                      axis.line = element_blank(),
                      axis.title = element_blank(),
                      axis.ticks = element_blank(),
                      axis.text = element_blank(),
                      legend.position = "bottom",
                      legend.title = element_blank(),
                      legend.key.width = unit(2, "cm"),
                      legend.text = element_text(size = 14),
                      plot.title = element_text(size = 20),
                      plot.subtitle = element_text(size = 14))

```

```{r global_options, include=FALSE}
opts_chunk$set(cache = FALSE, echo = FALSE, warning = FALSE,
               message = FALSE, out.height = "100%", out.width = "100%")
```

# Most recent data

```{r recent}
# Add in aggregated data ...
gg_first_recent <- j6 %>% 
  group_by(DISTRICT) %>% 
  mutate(chap_12_year = zoo::rollsumr(impute, k = 4, na.rm = T, na.pad = T),
         chap_12_change = chap_12_year - dplyr::lag(chap_12_year, 4),
         chap_12_rate = 10000*chap_12_year / farms_impute) %>% 
  filter(DATE == max(DATE)) %>% 
  right_join(gg_base)

states_recent <- j6 %>% 
  rename(id = STATE) %>% 
  group_by(id, DATE) %>% 
  summarise(impute = sum(impute, na.rm = T), farms_state = mean(farms_state, na.rm = T)) %>% 
  ungroup() %>% 
  group_by(id) %>% 
  mutate(chap_12_year = zoo::rollsumr(impute, k = 4, na.rm = T, na.pad = T),
         chap_12_change = chap_12_year - dplyr::lag(chap_12_year, 4),
         chap_12_rate = 10000*chap_12_year / farms_state) %>% 
  filter(DATE == max(DATE)) %>% 
  right_join(states)
gg_state_recent <- first %>% 
  fortify(region = "STATE") %>% 
  left_join(states_recent)

min_date <- min(filter(j6, DATE > max(DATE) - 367)$DATE) + 1
max_date <- max(j6$DATE)

sub_title <- paste0("From ", month(min_date, label = T, abbr = F),
                    " ", year(min_date), " through ",
                    month(max_date, label = TRUE, abbr = FALSE),
                    " ", year(max_date), ": ",
                    prettyNum(sum(j6$CHAP_12[j6$DATE > (min_date + 1)]),
                              big.mark = ","))

ggplot(gg_first_recent, aes(long, lat, group = group)) +
  geom_polygon(aes(fill = chap_12_year), color = "grey") +
  geom_path(data = gg_state_recent, color = "grey50") +
  geom_text(data = subset(gg_state_recent, !(id %in% new_england)),
            aes(x, y, label = prettyNum(round(chap_12_year), big.mark = ",")),
            check_overlap = T, size = 6, fontface = "bold") +
  labs(title = "Total Farm Bankruptcies Filed", 
       subtitle = sub_title) +
  scale_fill_gradient(low = "white", high = "red", #limits = c(0, 1000),
                      oob = squish, label = comma) +
  bank_theme
ggsave(paste0(figures, "/recent_raw.png"), width = 13.3, height = 10)
```


```{r recent-rate}
sub_title <- paste0("From ", month(min_date, label = T, abbr = F),
                    " ", year(min_date), " through ",
                    month(max_date, label = TRUE, abbr = FALSE),
                    " ", year(max_date), ": ",
                    prettyNum(round(10000*sum(j6$CHAP_12[j6$DATE > (min_date + 1)]) /
                                      sum(j6$farms_impute[j6$DATE == max_date], na.rm = T), 2)))

ggplot(gg_first_recent, aes(long, lat, group = group)) +
  geom_polygon(aes(fill = chap_12_rate), color = "grey") +
  geom_path(data = gg_state_recent, color = "grey50") +
  geom_text(data = subset(gg_state_recent, !(id %in% new_england)),
            aes(x, y, label = prettyNum(round(chap_12_rate, digits = 2), big.mark = ",")),
            check_overlap = T, size = 6, fontface = "bold") +
  labs(title = "Total Farm Bankruptcies Filed per 10,000 Farms", 
       subtitle = sub_title) +
  scale_fill_gradient(low = "white", high = "red", limits = c(0, 10),
                      oob = squish, label = comma) +
  bank_theme
ggsave(paste0(figures, "/recent_rate.png"), width = 13.3, height = 10)
```

```{r recent-rate-state}
sub_title <- paste0("From ", month(min_date, label = T, abbr = F),
                    " ", year(min_date), " through ",
                    month(max_date, label = TRUE, abbr = FALSE),
                    " ", year(max_date), ": ",
                    prettyNum(round(10000*sum(j6$CHAP_12[j6$DATE > (min_date + 1)]) /
                                      sum(j6$farms_impute[j6$DATE == max_date], na.rm = T), 2)))

ggplot(gg_state_recent, aes(long, lat, group = group)) +
  geom_polygon(aes(fill = chap_12_rate), color = "grey") +
  geom_path(data = gg_state_recent, color = "grey50") +
  geom_text(data = subset(gg_state_recent, !(id %in% new_england)),
            aes(x, y, label = prettyNum(round(chap_12_rate, digits = 2), big.mark = ",")),
            check_overlap = T, size = 6, fontface = "bold") +
  labs(title = "Total Farm Bankruptcies Filed per 10,000 Farms", 
       subtitle = sub_title) +
  scale_fill_gradient(low = "white", high = "red", limits = c(0, 10),
                      oob = squish, label = comma) +
  bank_theme
ggsave(paste0(figures, "/recent_rate_state.png"), width = 13.3, height = 10)
```


```{r recent-change}
sub_title <- paste0("From ", month(min_date, label = T, abbr = F),
                    " ", year(min_date), " through ",
                    month(max_date, label = TRUE, abbr = FALSE),
                    " ", year(max_date), ": ",
                    prettyNum(2*sum(j6$CHAP_12[j6$DATE > (min_date + 1)]) - sum(j6$CHAP_12[j6$DATE > (min_date - 365)]),
          big.mark = ","))

ggplot(gg_first_recent, aes(long, lat, group = group)) +
  geom_polygon(aes(fill = chap_12_change), color = "grey") +
  geom_path(data = gg_state_recent, color = "grey50") +
  geom_text(data = subset(gg_state_recent, !(id %in% new_england)),
            aes(x, y, label = prettyNum(round(chap_12_change), big.mark = ",")),
            check_overlap = T, size = 6, fontface = "bold") +
  labs(title = "Change In Total Farm Bankruptcies Filed", 
       subtitle = sub_title) +
  scale_fill_viridis_c(option = "E") +
  bank_theme
ggsave(paste0(figures, "/recent_change.png"), width = 13.3, height = 10)
```

# General Maps of Interest

All bankruptcy filings since BAPCPA came into effect as a rate:

```{r bapcpa}
sub_title <- paste0("Annualized from January 2006 through ",
                    month(max(j6$DATE), label = TRUE, abbr = FALSE),
                    " ", year(max(j6$DATE)), ": ",
                    round(4*(10000)*sum(j6$CHAP_12[j6$YEAR > 2005]) / 
                            sum(j6$farms_impute[j6$YEAR > 2005], na.rm = T), 2))

ggplot(gg_first_bapcpa, aes(long, lat, group = group)) +
  geom_polygon(aes(fill = b_rate), color = "grey") +
  geom_path(data = gg_state_bapcpa, color = "grey50") +
  geom_text(data = subset(gg_state_bapcpa, !(id %in% new_england)),
            aes(x, y, label = round(b_rate, 2)),
            check_overlap = T, size = 6, fontface = "bold") +
  labs(title = "Farm Bankruptcies filed per 10,000 farms", 
       subtitle = sub_title) +
  scale_fill_gradient(low = "white", high = "red",
                      limits = c(0, 10), oob = squish) +
  bank_theme
ggsave(paste0(figures, "/bapcpa_rates.png"), width = 13.3, height = 10)
```

Map generally used in the agricultural outlook meeting at Ohio State:

```{r deans}
gg_state_bapcpa$var = if_else(gg_state_bapcpa$id == "OHIO", "ohio", "rest")

ggplot(gg_first_bapcpa, aes(long, lat, group = group)) +
  geom_polygon(aes(fill = b_rate), color = "grey") +
  geom_path(data = gg_state_bapcpa, color = "grey50") +
  geom_text(data = subset(gg_state_bapcpa, !(id %in% new_england)),
            aes(x, y, label = round(b_rate, 2), size = var, alpha = var),
            check_overlap = T, fontface = "bold") +
  labs(title = "Farm Bankruptcy Rates",
       subtitle =  paste0("national rate: ",
                          round(4*(10000)*sum(j6$CHAP_12[j6$YEAR > 2005]) /
                                  sum(j6$farms_impute[j6$YEAR > 2005], na.rm = T),
                                2))) +
  scale_fill_gradient(low = "white", high = "red",
                      limits = c(0, 10), oob = squish) +
  scale_size_manual(values = c("rest" = 4, "ohio" = 10)) +
  scale_alpha_manual(values = c("rest" = 0.5, "ohio" = 1)) +
  guides(size = FALSE, alpha = FALSE) +
  bank_theme +
  theme(plot.title = element_text(size = 48),
        plot.subtitle = element_text(size = 24))
ggsave(paste0(figures, "/bapcpa_rates_dean.png"), width = 13.3, height = 10)
```

Raw data of bankruptcy filings since BAPCPA was enacted:

```{r bapcpa-count}
sub_title <- paste0("From January 2006 through ",
                    month(max(j6$DATE), label = TRUE, abbr = FALSE),
                    " ", year(max(j6$DATE)), ": ",
                    prettyNum(sum(j6$CHAP_12[j6$YEAR > 2005]),
                              big.mark = ","))

ggplot(gg_first_bapcpa, aes(long, lat, group = group)) +
  geom_polygon(aes(fill = CHAP_12), color = "grey") +
  geom_path(data = gg_state_bapcpa, color = "grey50") +
  geom_text(data = subset(gg_state_bapcpa, !(id %in% new_england)),
            aes(x, y, label = prettyNum(round(CHAP_12), big.mark = ",")),
            check_overlap = T, size = 6, fontface = "bold") +
  labs(title = "Total Farm Bankruptcies Filed", 
       subtitle = sub_title) +
  scale_fill_gradient(low = "white", high = "red", #limits = c(0, 1000),
                      oob = squish, label = comma) +
  bank_theme
ggsave(paste0(figures, "/bapcpa_raw.png"), width = 13.3, height = 10)
```

# Historical

Since chapter 12 was an available bankruptcy option for farmers in October of 1986:

```{r albers}

first <- counties_composite("aeqd")

first <- merge(first, dists)

gg_base <- fortify(first, region = "DISTRICT") %>%
  rename(DISTRICT = id)

# Add in aggregated data ...
gg_first <- j6 %>% 
  group_by(DISTRICT) %>% 
  summarise(b_rate = 4*(10000)*sum(impute, na.rm = T) /
              sum(farms_impute, na.rm = T),
            CHAP_12 = sum(impute, na.rm = T),
            farms  = mean(farms_impute, na.rm = T)) %>%
  right_join(gg_base)


states  <- usa_composite("aeqd")
states <- data.frame(toupper(states$name), coordinates(states),
                     stringsAsFactors = F)
names(states) <- c("id", "x", "y")
states <- j6 %>% 
  rename(id = STATE) %>% 
  group_by(id) %>% 
  summarise(b_rate = 4*(10000)*sum(impute, na.rm = T) /
              sum(farms_impute, na.rm = T),
            CHAP_12 = sum(impute, na.rm = T)) %>%
  right_join(states)
gg_state <- first %>% 
  fortify(region = "STATE") %>% 
  left_join(states)


# Remove the new england states
new_england <- c("CONNECTICUT", "RHODE ISLAND", "VERMONT",
                 "DISTRICT OF COLUMBIA", "DELAWARE")
sub_title <- paste0("Annualized from October 1986 through ",
                    month(max(j6$DATE), label = TRUE, abbr = FALSE),
                    " ", year(max(j6$DATE)), ": ",
                   round(4*(10000)*sum(j6$impute, na.rm = T) /
                           sum(j6$farms_impute, na.rm = T), 2))

ggplot(gg_first, aes(long, lat, group = group)) +
  geom_polygon(aes(fill = b_rate), color = "grey") +
  geom_path(data = gg_state, color = "grey50") +
  geom_text(data = subset(gg_state, !(id %in% new_england)),
            aes(x, y, label = round(b_rate, 2)),
            check_overlap = T, size = 6, fontface = "bold") +
  labs(title = "Farm Bankruptcies filed per 10,000 farms", 
       subtitle = sub_title) +
  scale_fill_gradient(low = "white", high = "red",
                      limits = c(0, 10), oob = squish) +
  bank_theme
ggsave(paste0(figures, "/historical_rates.png"), width = 13.3, height = 10)
```

Historical data, raw:

```{r albers-count}
sub_title <- paste0("From October 1986 through ",
                    month(max(j6$DATE), label = TRUE, abbr = FALSE),
                    " ", year(max(j6$DATE)), ": ",
                    prettyNum(sum(j6$impute, na.rm = T), big.mark = ","))

ggplot(gg_first, aes(long, lat, group = group)) +
  geom_polygon(aes(fill = CHAP_12), color = "grey") +
  geom_path(data = gg_state, color = "grey50") +
  geom_text(data = subset(gg_state, !(id %in% new_england)),
            aes(x, y, label = prettyNum(round(CHAP_12), big.mark = ",")),
            check_overlap = T, size = 6, fontface = "bold") +
  labs(title = "Total Farm Bankruptcies Filed", 
       subtitle = sub_title) +
  scale_fill_gradient(low = "white", high = "red",
                      # limits = c(0, 10000), oob = squish,
                      label = comma) +
  bank_theme
ggsave(paste0(figures, "/historical_raw.png"), width = 13.3, height = 10)
```

Historical rates of bankruptcy, animated (note, Arkansas changed its reporting structure in 2018 going from reporting its districts separately to combined reporting):

```{r animate-albers}
gg_anime <- j6 %>% 
  ungroup() %>% 
  group_by(DISTRICT, YEAR) %>% 
  summarise(b_rate = 4*(10000)*sum(impute, na.rm = T) /
              sum(farms_impute, na.rm = T),
            farms  = mean(farms_impute, na.rm = T)) %>%
  right_join(gg_base)

anim <- ggplot(gg_anime, aes(long, lat, group = group)) +
  geom_polygon(aes(fill = b_rate), color = "black") +
  geom_path(data = gg_state, color = "white") +
  transition_manual(YEAR) +
  labs(title = "Bankruptcies filed in: {current_frame}", 
       subtitle = "Annualized per 10,000 farms") +
  scale_fill_viridis_c(limits = c(0, 20), oob = squish) +
  bank_theme
animate(anim, width = 1024, height = 768)
# Uncomment to save
# anim_save(paste0(figures, "/historical-animate.gif"))
```

Animated, but with red scale:

```{r animate-albers-red}
anim <- ggplot(gg_anime, aes(long, lat, group = group)) +
  geom_polygon(aes(fill = b_rate), color = "grey") +
  geom_path(data = gg_state, color = "grey50") +
  transition_manual(YEAR) +
  labs(title = "Bankruptcies filed in: {current_frame}", 
       subtitle = "Annualized per 10,000 farms") +
  scale_fill_gradient(low = "white", high = "red",
                      limits = c(0, 20), oob = squish) +
  bank_theme
animate(anim, width = 1024, height = 768)
# Uncomment to save
# anim_save(paste0(figures, "/historical-animate-red.gif"))
```

